Tilting at Algorithmic Windmills

### 2013-05-05 Tilting/paper.tex
WIP: notes on this paper

\usepackage{color}
\usepackage{multirow,booktabs,ctable,array}
\usepackage{lscape}
\usepackage{amsmath}
\usepackage{lineno}
\usepackage{ulem}
\usepackage{setspace}
\usepackage{listings}
\usepackage{float}
\usepackage{listings}
\usepackage{color,colortbl}
\usepackage{rccol}
\usepackage[table]{xcolor}

@@

  \item Great resources for code-sharing
		  \item github
		  \item NITRC
		  \item ITK

>>>>

\usepackage{color,hyperref}
\usepackage{multirow,booktabs,ctable,array}
\usepackage{lscape}
\usepackage{amsmath}
\usepackage{lineno}
\usepackage{ulem}
\usepackage{setspace}
\usepackage{listings}
\usepackage{float}
\usepackage{listings}
\usepackage{color,colortbl}
\usepackage{rccol}
\usepackage[table]{xcolor}

@@

  \item Collaborators should help verify findings by repeating a
(representative subset of a) study independently, from scratch,
preferably on another computer perhaps even with a different operating
system.  A scientist can do this him/herself as well.  Personal
experience suggests that this procedure will often uncover coding
errors sometimes simply by forcing one to reread code or scripts again
or clarify documentation.

  \item
    \textcolor{blue}{\href{http://en.wikipedia.org/wiki/Accuracy_and_precision}{Accuracy
        and precision (link)}} --- most studies ignore precision.  it
    is critical in longitudinal studies.   precision is impacted by
    parameter choices as well as computational architecture
    (Freesurfer paper)

   \item parameters impact accuracy - e.g. clarkson's paper vs our
     recent tuning of DiReCT parameters w.r.t. expected thickness values.

  \item  Biological plausibility is important---a more accurate method
    may produce less biologically plausible results.
    Cross-referencing with other fields is critical e.g. patterns of
    MRI atrophy should match pathology distribution.  There is an art
    to this, of course.

  \item Prediction---an algorithm that yields a ``more significant''
    result is not always better.  might mean ``finds more effected
    areas'' or smaller p-values.  Testing prediction is complements
    studies of significance and cumulative distribution functions.

  \item Verification is supported by open science technology for
    sharing data and code.

   \item Great resources for data-sharing:
  	\begin{itemize}
	   \item figshare
           \item MIDAS 
           \item slicedrop
           \item R 
        \end{itemize}

  \item Great resources for code-sharing
  	\begin{itemize}
		  \item github
		  \item NITRC
		  \item ITK
		\end{itemize}
\end{itemize}
